STA302 Final Project Proposal

### 2024-10-11 paper/proposal.qmd
Update proposal.qmd

# Fit multiple linear regression model
model <- lm(average_playtime ~ price + positive_ratings + negative_ratings + developer + owners)

# Create Residuals vs Fitted Scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

@@

# Create Residuals vs each Quantitative Predictor scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

@@

# Create BoxPlot to check assumptions for Categorical Predictors

@@

# Create Normal QQ Plot to check Normality assumption

>>>>

## Fit multiple linear regression model
model <- lm(average_playtime ~ price + positive_ratings + negative_ratings + developer + owners)

## Create Residuals vs Fitted Scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

@@

## Create Residuals vs each Quantitative Predictor scatterplot to check Linearity, Uncorrelated Errors, and Constant Variance

@@

## Create BoxPlot to check assumptions for Categorical Predictors

@@

## Create Normal QQ Plot to check Normality assumption
